%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% Change social information separator if needed
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\input{cv-sec/info}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Novo Nordisk Engineering\\Virum, Denmark}
  {Global IT Department}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Student Assistant - Global IT Projects}
% How the letter is opened
\letteropening{Dear Mr. Høst Hansen,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information (alignment: R=right, L=left, C=center)
\makecvheader[R]

% Print the footer with three arguments (<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Federico Marra~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am Federico Marra, a Master’s student in Computer Science and Engineering at the Technical University of Denmark (DTU). My academic background in Data Security, Software Engineering, and Program Verification has provided me with a solid technical foundation. In addition, my experience as a Software Engineer at SNAP4 S.r.l. has honed my ability to manage projects, collaborate in agile teams, and develop innovative solutions. On a personal note, being diabetic has further motivated me to contribute to healthcare-related projects, as I understand firsthand the importance of quality and efficiency in systems that impact patient lives.

\lettersection{Why Novo Nordisk Engineering?}
I am excited by the opportunity to join Novo Nordisk Engineering, a leader in designing and building state-of-the-art pharma facilities that serve millions of patients worldwide. The prospect of supporting the Global IT team in planning, coordinating, and executing projects is particularly appealing. I am drawn to an environment that values collaboration, innovation, and a noble cause—ensuring that digital solutions empower both employees and end-users in a complex, international setting.

\lettersection{Why Me?}
My strong technical and organizational skills, coupled with my passion for project management, make me an excellent fit for this role. I have practical experience with software development and automation, and I am adept at supporting day-to-day IT project tasks such as preparing communications, scheduling meetings, and coordinating change management activities. Furthermore, my proactive and solution-oriented mindset enables me to thrive in dynamic environments. Being diabetic, I have a personal commitment to making a tangible impact in healthcare, and I am eager to contribute to projects that improve efficiency and quality in global IT operations at Novo Nordisk Engineering.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
