%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


\input{cv-sec/info}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Mærsk Mc-Kinney Moller Center for Zero Carbon Shipping}
  {Marmorvej 8 2100 København Ø}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Student Assistant – Transition Analytics \& Insights – Software Development}
% How the letter is opened
\letteropening{Dear Mr. Frederik Winkel Lehn}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Federico Marra~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am Federico Marra, a Master's student in Computer Science and Engineering at the Technical University of Denmark (DTU). With a solid foundation in software development, I have expertise in Python, Java, C, C++, and TypeScript, complemented by experience with tools like Docker and GitHub. My DTU academic journey has equipped me with knowledge in Data Security, Model Predictive Control, Program Verification, and Software Engineering. Furthermore, my role as a Software Engineer at SNAP4 S.r.l. has strengthened my ability to collaborate effectively in dynamic environments and work with new technologies to develop scalable applications. Passionate about problem-solving and innovation, I am eager to apply my skills and contribute meaningfully to impactful projects.

\lettersection{Why Mærsk Mc-Kinney Moller Center for Zero Carbon Shipping?}
The Mærsk Mc-Kinney Moller Center for Zero Carbon Shipping stands out as a pioneering force in decarbonizing the maritime industry. Your commitment to sustainability and cutting-edge technology strongly aligns with my values, aspirations and worries about climate-change. The opportunity to work within a multidisciplinary team on a project with tangible global impact is highly motivating for me. I am particularly drawn to the Transition Analytics \& Insights team, where I am eager to engage with NavigaTE. The center’s emphasis on collaboration, learning and innovation presents an ideal environment for me to grow as a software developer while actively contributing to an industry and world critical transformation.

\lettersection{Why Me?}
With a strong background in software engineering and hands-on experience in Python and Git/Github, I am well-suited for the role of Student Assistant in Software Development. My previous projects, including process mining tools, authentication systems, and predictive control implementations, have refined my ability to write efficient and maintainable code. Additionally, my problem-solving skills, developed through tackling mathematical and algorithmic challenges, enable me to optimize and enhance existing systems. Beyond technical proficiency, I take pride in my proactive approach, curiosity, and commitment to continuous learning, qualities that I think best align with the center’s culture. I am eager to contribute my skills, collaborate with experts, and support the mission of achieving zero-carbon shipping.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}