%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% Change social information separator if needed
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\input{cv-sec/info}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Demant A/S\\Smørum, Denmark}
  {Embedded Bluetooth Team}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Student Assistant - Embedded Bluetooth Team}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information (alignment: R=right, L=left, C=center)
\makecvheader[R]

% Print the footer with three arguments (<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Federico Marra~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am Federico Marra, a Master’s student in Computer Science and Engineering at the Technical University of Denmark (DTU). My academic background in Data Security, Software Engineering, and Program Verification has provided me with a solid technical foundation. In addition, my hands-on experience as a Software Engineer at SNAP4 S.r.l. has honed my ability to develop innovative solutions using languages such as C, Python, and other modern programming tools. I am enthusiastic about embedded systems and the role of continuous integration in delivering reliable software.

\lettersection{Why Demant?}
I am excited by the opportunity to join Demant—a world-leading hearing healthcare and technology group—and contribute to the development of future connectivity solutions for hearing aids. Your mission to enable the hearing impaired to engage fully in society resonates deeply with me. The chance to work with the latest embedded technologies and to improve the build and test pipeline for Bluetooth connectivity aligns perfectly with my technical interests and career aspirations. Moreover, I appreciate Demant's commitment to diversity and inclusion.

\lettersection{Why Me?}
I bring strong programming skills in C and Python, hands-on experience with embedded systems, and a proactive approach to problem-solving. My background in software development, combined with practical experience in continuous integration and automated testing, makes me well-suited for improving the quality of your build and test pipeline. I am comfortable working in agile teams, actively participating in standups and collaborative problem-solving sessions. I am confident that my technical expertise and enthusiasm will contribute to delivering a versatile and stable Bluetooth solution for Demant's innovative hearing instrument technologies.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
