%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {SNAP4 S.r.l.} % Organization
    {Software Engineer} % Job title
    {Sesto Fiorentino, Florence, Italy} % Location
    {March 2024 - August 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I developed \textit{eShare in a Snap}, first car sharing and car pooling app in Italy.}
        \item {\textbf{Technology:} Typescript, Angular, Ionic, Firebase, Capacitor}
        \item {\textbf{eShare in a Snap:} \href{https://www.snap4.eu/products/eshare-in-a-snap-sustainable-mobility.html}{https://www.snap4.eu/products/eshare-in-a-snap-sustainable-mobility.html}}
        \item {\textbf{eShare in a Snap App Store:} \href{https://apps.apple.com/us/app/eshare-in-a-snap/id6572306097}{https://apps.apple.com/us/app/eshare-in-a-snap/id6572306097}}
        \item {\textbf{eShare in a Snap Google Play Store:} \href{https://play.google.com/store/apps/details?id=com.snap4.eShare_in_a_Snap&hl=en}{https://play.google.com/store/apps/details?id=com.snap4.eShare\_in\_a\_Snap}}
        %\item {\textbf{eShare in a Snap GitHub repository:} \href{https://github.com/snap4srl/eshare-in-a-snap}{https://github.com/snap4srl/eshare-in-a-snap}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Private Tutor} % Organization
    {Private Tutor} % Job title
    {Florence, Italy} % Location
    {March 2023 - February 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I tutored students in middle school mathematics, high school mathematics, and fundamentals of informatics at the university level for three diﬀerent individuals.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Italian Republic} % Organization
    {Election Scrutineer secretary} % Job title
    {Florence, Italy} % Location
    {September 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I served as the secretary in charge of counting ballots for international votes during the Italian Parliament election on 25$^{\text{th}}$ of September 2022.}
      \end{cvitems}
    }
    \begin{comment}

%---------------------------------------------------------
  \cventry
    {School-Work Alternance} % Job title
    {Italian School} % Organization
    {Florence, Italy} % Location
    {June 2017 - June 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities  
        \item {\textbf{Observatory in Chianti:}} Design of an educational path summarizing the history of the universe. Tasks included brainstorming, selecting key eras, creating bilingual content (Italian and English), and designing panel supports. Skills acquired: deep understanding of the universe's history, firsthand observation of an astrophysicist’s work.
        \item {\textbf{University Hospital Company Meyer:}} Observation of pediatricians in the Rheumatology Department, assisting with patient visits and understanding the medical profession. Skills acquired: insights into the challenges of being a doctor, knowledge of rheumatology, including conditions like Lupus and Juvenile Idiopathic Arthritis (JIA).
        \item {\textbf{Caritas Florence:}} Creation of a file compiling the services offered by Caritas Firenze, mapping various locations in Florence and the positions of clothing recycling bins. Skills acquired: basic use of Photoshop and GIMP, understanding of the internal organization of the association.
      \end{cvitems}
    }
        
    \end{comment}
%---------------------------------------------------------
\end{cventries}
